\documentclass[10pt,a4paper]{article}
    \usepackage{fullpage}
    \usepackage{amsmath}
    \usepackage{amssymb}
    \usepackage{textcomp}
    \usepackage[utf8]{inputenc}
    \usepackage[T1]{fontenc}
    \textheight=10in
    \pagestyle{empty}
    \raggedright
    \usepackage[left=0.8in,right=0.8in,bottom=0.8in,top=0.8in]{geometry}

    %\renewcommand{\encodingdefault}{cg}
%\renewcommand{\rmdefault}{lgrcmr}

\def\bull{\vrule height 0.8ex width .7ex depth -.1ex }

% DEFINITIONS FOR RESUME %%%%%%%%%%%%%%%%%%%%%%%

\newcommand{\area} [2] {
    \vspace*{-9pt}
    \begin{verse}
        \textbf{#1}   #2
    \end{verse}
}

\newcommand{\lineunder} {
    \vspace*{-8pt} \\
    \hspace*{-18pt} \hrulefill \\
}

\newcommand{\header} [1] {
    {\hspace*{-18pt}\vspace*{6pt} \textsc{#1}}
    \vspace*{-6pt} \lineunder
}

\newcommand{\employer} [3] {
    { \textbf{#1} (#2)\\ \underline{\textbf{\emph{#3}}}\\  }
}

\newcommand{\contact} [3] {
    \vspace*{-10pt}
    \begin{center}
        {\Huge \scshape {#1}}\\
        #2 \\ #3
    \end{center}
    \vspace*{-8pt}
}

\newenvironment{achievements}{
    \begin{list}
        {$\bullet$}{\topsep 0pt \itemsep -2pt}}{\vspace*{4pt}
    \end{list}
}

\newcommand{\schoolwithcourses} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
    \vspace*{5pt}
}

\newcommand{\school} [4] {
    \textbf{#1} #2 $\bullet$ #3\\
    #4 \\
}
% END RESUME DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%

    \begin{document}
\vspace*{-40pt}

    

%==== Profile ====%
\vspace*{-10pt}
\begin{center}
	{\Huge \scshape {Lokesh Sanapalli}}\\
	Bengaluru, India $\cdot$ hi@lokesh1729.com $\cdot$ 9538779797 $\cdot$ https://lokesh1729.com\\
\end{center}

\header{Headline}
results-driven software engineering leader \textbar{} 10+ years of experience in building scalable, resilient, low-latency distributed systems \textbar{} proven track record in leading and managing teams, designing end-to-end architectures, and delivering complex projects irrespective of tech stack\\
\vspace*{2mm}

%==== Education ====%
\header{Education}
\textbf{RGUKT IIIT Nuzvid}\hfill Nuzvid, Andhra Pradesh\\
B.Tech Computer Science \textit{GPA: 8.2} \hfill July 2009 - May 2015\\
\vspace{2mm}

%==== Experience ====%
\header{Work Experience}
\vspace{1mm}
\textbf{Moneyview} \hfill Bengaluru\\
\textit{Engineering Manager} \hfill May 2025 - Present\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
    \item Owned HL/LAP, platform charters for the cross-sell pod, leading 9 backend engineers, 1 frontend engineer, and 2 DevOps engineers to deliver critical business, security, and technology initiatives.
\end{itemize}

\textbf{Moneyview} \hfill Bengaluru\\
\textit{Lead Software Engineer (Unofficial Engineering Manager)} \hfill January 2024 - April 2025\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Built a team of \textbf{10 engineers} for the Cross-Sell pod from scratch. Acted as a pseudo engineering manager (hired 5 engineers), conducted regular 1:1s, provided actionable feedback, and \textbf{led bi-annual performance reviews}. Mentored and coached \textbf{3 engineers to consistently exceed expectations}.

    \item Built and scaled the Home Loans/LAP product from \textbf{0 to 10 Cr+} in monthly disbursals, integrating with \textbf{15+ partners}. Played a pivotal role in product development including \textbf{partner integrations}, internal \textbf{ops workflows}, and \textbf{user experience journey}. Designed reusable integration frameworks and led several ops-critical initiatives including Freshsales integration and a custom CRM with WhatsApp chat support.

    \item Developed and launched the Credit Cards product from \textbf{0 to 2K+ disbursals/month}. Led the system design with \textbf{5+ partners' native API integrations}, and drove development of a scalable MIS email automation engine processing \textbf{1M+ partner records} monthly. Contributed to product development spanning \textbf{partner onboarding}, \textbf{ops workflows}, and the \textbf{customer journey}.

    \item Spearheaded the launch of the Digital Gold product (SIP, one-time, gifting), scaling it from \textbf{0 to 10K daily transactions}, significantly boosting user engagement on the MoneyView platform.

    \item Established and scaled core engineering processes — including structured on-call rotation process, system design reviews, multi-level code reviews (with pair programming), and \textbf{RCA workflows} — to strengthen team reliability, ownership, and engineering excellence.

    \item Led technical execution and cross-functional delivery through architecture/code reviews, mentoring, \textbf{sprint planning, retrospectives, and effective stakeholder collaboration} — fostering an engineering-first culture with strong operational processes.

    \item Defined and executed critical observability and reliability initiatives — set up full-stack observability \textbf{Datadog and Kibana}, implemented \textbf{circuit breaker} for all HTTP clients, migrated outgoing HTTP logging from RDS to S3 for cost efficiency, and optimized DB performance via reader-writer separation improving higher reliability and future scalability.

    \item Trained engineers on leveraging AI-assisted tools such as \textbf{Qodo, Cursor, and GitHub Copilot}, resulting in measurable improvements in development speed, code quality, and overall engineering productivity.
\end{itemize}

\textbf{Moneyview} \hfill Bengaluru\\
\textit{Lead Software Engineer} \hfill May 2023 - December 2024\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
    \item Architected continous archival process using percona tools for high write throughput tables in loan origination system.

    \item Re-architected and rewritten loan insurance flows by solving multiple entries due to concurrency.

    \item Architected HTTP callback system for loan sourcing partners. Executed by mentoring 2 engineers.

    \item Implemented connection pooling for legacy memcached library in loan origination monolith system.

    \item Architected and implemented a sourcing partner portal integrated with the loan origination system, sourcing partner system streamlining partner communication and simplifying partner configuration.

    \item Have setup code review, design review processes within the team ensuring high code quality standards.

    \item Defined and executed critical observability and reliability initiatives — set up full-stack observability for loan origination systems using \textbf{Datadog and Kibana}.

    \item Designed and implemented an org-wide third-party degradation detection system using \textbf{Datadog and Micrometer}, improving user experience and conversion funnel health.
\end{itemize}

\textbf{Licious} \hfill Bengaluru\\
\textit{Lead Software Engineer} \hfill Nov 2021 - April 2023\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Improved the existing product listing APIs by reducing P99 latency from \textbf{1.5 seconds to 200ms} by creating a new microservice called Discovery. Led HLD, LLD, implementation, and delivery end-to-end, while \textbf{mentoring 3 junior engineers throughout the project lifecycle}.
	\item \textbf{Rearchitected and rewritten} the Review \& Rating microservice (originally in Node.js), optimizing both data storage and latency. \textbf{Closely collaborated with product stakeholders to align technical design with business goals} and ensure smooth rollout.
	\item Revamped the milestone-based rewards system (originally in Golang) to support spin wheel campaigns, leading to improved customer retention funnels.
	\item Led and delivered multiple growth team initiatives to transition from a monolithic to a microservices architecture.
\end{itemize}
\textbf{Akamai} \hfill Bengaluru, India\\
\textit{Senior Software Engineer} \hfill May 2018 - Nov 2021\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Designed the report automation platform from scratch as part of the Managed Security Product team, including HLD and LLD.
	\item Built a data aggregation pipeline using \textbf{Python, Celery, and RabbitMQ} to collect data from multiple sources
	\item Improved Celery worker throughput and report generation by \textbf{3x} by switching to a \textbf{Gevent-based I/O-optimized} implementation.
\end{itemize}
\textbf{Bigbasket} \hfill Bengaluru, India\\
\textit{Software Engineer II} \hfill Nov 2016 - May 2018\\
\vspace{-1mm}
\begin{itemize} \itemsep 1pt
	\item Designed and implemented backend APIs for features like cancellation charges and slot availability.
	\item Rewrote and optimized APIs in Python, Django and Node.js to enhance reliability and performance of the infrastructure.
\end{itemize}
\textbf{Cigital} \hfill Bengaluru, India\\
\textit{Associate Software Engineer} \hfill Nov 2015 - Jun 2016\\
\textbf{Techmahindra} \hfill Hyderabad\\
\textit{Associate Software Engineer} \hfill July 2015 - Oct 2015\\

\header{Skills}
\begin{tabular}{ l l }
	Programming Languages \& Frameworks: & Python, Django, Javascript, Node.js, Java, Spring Boot            \\
	Backend Technologies:                & Kafka, Rabbitmq, Redis, AWS, Docker, Kubernetes, Debezium         \\
	Databases:                           & MySQL, PostgreSQL, MongoDB, ElasticSearch                         \\
	Frontend:                            & HTML5, CSS3, Javascript, Tailwind CSS, React                      \\
	Others:                              & Problem Solving, Data Structures, Algorithms, Agile Methodologies \\
\end{tabular}
\vspace{2mm}

\header{Awards}
{\textbf{Rookie Rockstar}} {\sl Moneyview} \\
Awarded \textquotesingle{}Rookie Rockstar\textquotesingle{} for establishing an engineering-first culture, driving disruptive change, and redefining team goals to align with high-impact delivery.\\
\vspace*{2mm}
{\textbf{Circle of Excellence}} {\sl Moneyview} \\
Awarded \textquotesingle{}Circle of Excellence\textquotesingle{} for successful delivery and execution of key products including Digital Gold, Home Loans, and Credit Cards.\\
\vspace*{2mm}

\ 
\end{document}